---
title: "Wine_network1"
author: "Bonnie Lin"
date: "11/29/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(network)
library(mosaic)
library(sna)
library(ggplot2)
library(stringr)
library(readr)
library(dplyr)
library(FactoMineR)
library(igraph)
library(cluster)
library(xtable)
library(sm)
```

## Sources for Writeup 
https://www.sixhat.net/finding-communities-in-networks-with-r-and-igraph.html
https://www.rdocumentation.org/packages/sm/versions/2.2-5.4/topics/sm.density.compare

## Wine dataset prep for MFA
```{r}
set.seed(20000000)

wine_orig <- read_csv("winemag-data-130k-v2.csv")
#complete_cases_wine <- na.omit(wine)
#complete_case_wine_count <- nrow(complete_cases_wine)

interestedvars <- wine_orig %>%
    mutate(year = str_extract(wine_orig$title, "[1|2][0|1|9][0-9][0-9]")) %>%
  select(price, year, variety, country, points) %>%
  na.omit()

wine <- interestedvars %>% 
  mutate(year = as.numeric(year), #convert data type is needed for mfa
         price = as.numeric(price),
         variety = as.factor(variety),
         country = as.factor(country)) %>%
  filter(country == "France") %>%
  distinct() %>% 
  sample_n(100) #too large data structure otherwise 

# 
# wine_subset <- wine[, c(-1, -3, -4, -11, -12, -14)]
# wine_reorder <- wine_subset[,c(1,4:6,2,3,9,7,8)] # prep for grouping 
## res = MFA(wine_reorder, group = c(4, 3, 2), type = c("n", "c", "n"), ncp = 3, name.group = c("place", "measure", "property")) # XX help with the last two groupings 
## plot(res,choix="ind",partial="all") ## XX help with interpretation 


## Annotation for MFA() function
#wine: the data set used
#group: a vector indicating the number of variables in each group
#type: the type of the variables in each group. "s" for scaled continuous variables, "c" for centered (unscaled) continuous variables and "n" for categorical variables
#ncp: number of dimensions kept in the result
#name.group: names of the groups
#num.group.sup: indexes of the supplementary groups

## Also, I tried FAMD() function from the FactoMineR package too but to no avail
## res2 <- FAMD(wine_reorder)
## Seems like we can tackle imputing the numerical data but I'm still not sure about imputing text data



### daisy function to find clusters
# wine_small <- wine_reorder[, c(1,5:7, 9)] %>%
#   mutate(country = as.factor(country),
#          variety = as.factor(variety))

d.wine <- daisy(wine[1:4], metric = "gower", stand = FALSE)
d.winemat <- as.matrix(d.wine)

## create edge matrix 
d.winemat.edge <- matrix(rep(0, 100^2), nrow = 100, ncol = 100)
  
for(i in 1:100){
  for(j in 1:100){
    d.winemat.edge[i,j] = ifelse(d.winemat[i,j] < 0.35, 0, 1)
  }
}
colnames(d.winemat.edge) = wine$
rownames(d.winemat.edge) = wine$year


# make into adjacency list
wine.diss <- data.frame(wine1=rownames(d.winemat.edge)[row(d.winemat.edge)], wine2=colnames(d.winemat.edge)[col(d.winemat.edge)], dist=c(d.winemat.edge)) 

wine.diss <- wine.diss %>%
 mutate(edge = ifelse(wine.diss$dist < firstq, 0, 1))
# 
# plot(density(wine.diss$dist))
# firstq <- summary(wine.diss$dist)[2]
# 
# adjlist <- by(wine.diss, wine.diss$wine1, function(x) x$wine2)
# 
# for (i in as.character(unique(wine.diss$wine1))) {
#    cat(i, ' -> ', adjlist[[i]], '\n')
# }
# 
# g1 <- graph_from_adj_list(adjlist, mode = "all") 
# plot(g1)
# g1 <- simplify(g1)
# plot(g1)
```

### Making the index
Make some index that allows two wine observations to be compared - a dissimiliarity of some sort; maybe via PCA if you know it (or I could help with it)

Questions -- 
once we have the influential variables from MFA or PCA... how do we quantify this? 

### Construct a wine network 
Compute the pairwise dissimilarity matrix and use it to construct a wine network - for example, if the dissimiliarity is less than 10, put an edge between the wine nodes.

```{r}
g1 <- graph_from_adjacency_matrix(d.winemat.edge, mode="upper")
plot(g1)
```

### Look for clusters 
Use a graph partitioning or other clustering on network algorithm to look for clusters, or do some other network analysis to look for hub nodes, or something. https://www.sixhat.net/finding-communities-in-networks-with-r-and-igraph.html 
The following four algorithms look for clusters: 

## Algorithm 1: Walktrap.community

```{r}
wt <- walktrap.community(g1)
membership(wt)
sizes(wt)
plot(wt,g1)
modularity(wt)

```


## Algorithm 2: Edge.betweenness.community

```{r}
# Now we have the merges/splits and we need to calculate the modularity
# for each merge for this we'll use a function that for each edge
# removed will create a second graph, check for its membership and use
# that membership to calculate the modularity
set.seed(495)
ebc <- edge.betweenness.community(g1)
mods <- sapply(0:ecount(g1), function(i){
  g2 <- delete.edges(g1, ebc$removed.edges[seq(length=i)])
  cl <- clusters(g2)$membership
  modularity(g1,cl)
})


# we can now plot all modularities
plot(mods, pch=100)
# Now, let's color the nodes according to their membership
g2<-delete.edges(g1, ebc$removed.edges[seq(length=which.max(mods)-1)])
V(g1)$color=clusters(g2)$membership
 
# Let's choose a layout for the graph
g1$layout <- layout.fruchterman.reingold
 
# plot it
plot(ebc, g1)
```



## Algorithm 3: Fastgreedy.community

```{r}
fc <- cluster_fast_greedy(g1)
membership(fc)
sizes(fc)
coords <- layout_with_fr(g1)
plot(g1, vertex.color=membership(fc), layout = coords)

#summary stats by cluster
wine$cluster <- as.factor(fc$membership)
 wine %>% 
  group_by(cluster) %>% 
  summarise(mean_price = mean(price),
            mean_year = mean(year),
            mean_points = mean(points))

 #population means 
mean(wine$price)
mean(wine$year)
mean(wine$points)
```

Gives us two clusters (~25:25)

## Algorithm 4: Spinglass.community

```{r}
spin <- spinglass.community(g1)
membership(spin)
sizes(spin)
plot(spin, g1)
```

### Visualizations for the clusters
A visual to display this that might allow the user to change how the network is constructed (change the dissimilarity) or at least view the clusters would be a good wrap-up visual.


```{r, echo=FALSE}
# promo <- matrix(c(6,0,1,3),ncol=2,byrow=TRUE)
# colnames(promo) <- c("Promoted","Not Promoted")
# rownames(promo) <- c("Contributed to Winner","Did Not Contribute to Winner")
# promo <- as.table(promo)

FC <- as.vector(membership(fc))
SPIN <- as.vector(membership(spin))
EBC <- as.vector(membership(ebc))

fc_spin_table <- tally(~FC + SPIN)
fc_spin_table

tally(~FC+EBC)

everything_table <- tally(~EBC + SPIN + FC)
everything_table
```

```{r,results='asis',tab.cap = NULL, echo = FALSE}
# print(xtable(promo, caption = "TABLE 1 Contribution by Promotion"), 
#     comment=FALSE, caption.placement = "top")
```      


## Filtering on the most popular wines
```{r}
popular5winefind <- interestedvars %>% 
  group_by(variety) %>% 
  summarise(n = n()) %>% 
  as.data.frame() %>% 
  arrange(., desc(n)) %>% 
  head(5)

popular5wine <- wine_orig %>%
    mutate(year = str_extract(wine_orig$title, "[1|2][0|1|9][0-9][0-9]"),
           price = as.numeric(price),
           year = as.numeric(price),
           country = as.factor(country)) %>%
  select(price, year, variety, country, points) %>%
  filter(variety %in% popular5winefind$variety) %>%
  distinct() %>% 
  na.omit() %>%
  sample_n(100)

popular5wine <- popular5wine[, c(1, 2, 4, 5, 3)] # prep for grouping 


d.wine.pop <- daisy(popular5wine[1:4], metric = "gower", stand = FALSE)
d.winemat.pop <- as.matrix(d.wine.pop)

## create edge matrix 
d.winemat.pop.edge <- matrix(rep(0, 100^2), nrow = 100, ncol = 100)
  

## with this seed, the mean is about 0.3345 
## the median is about 0.3316

for(i in 1:100){
  for(j in 1:100){
    d.winemat.pop.edge[i,j] = ifelse(d.winemat.pop[i,j] < 0.33, 0, 1)
  }
}
colnames(d.winemat.edge) = popular5wine$country
rownames(d.winemat.edge) = popular5wine$country

# make into adjacency matrix 
g1.pop <- graph_from_adjacency_matrix(d.winemat.pop.edge, mode="upper")
plot(g1.pop)

# try algorithms
wt.pop <- walktrap.community(g1.pop)
plot(wt.pop, g1.pop)

# # make into adjacency list
# wine.diss <- data.frame(wine1=rownames(d.winemat.edge)[row(d.winemat.edge)], wine2=colnames(d.winemat.edge)[col(d.winemat.edge)], dist=c(d.winemat.edge)) %>%
#    mutate(edge = ifelse(wine.diss$dist < firstq, 0, 1))
```


### Analysis on the most popular countries
```{r}
set.seed(20000000)

wine_orig <- read_csv("winemag-data-130k-v2.csv")
#complete_cases_wine <- na.omit(wine)
#complete_case_wine_count <- nrow(complete_cases_wine)

interestedvars <- wine_orig %>%
    mutate(year = str_extract(wine_orig$title, "[1|2][0|1|9][0-9][0-9]")) %>%
  select(price, year, variety, country, points) %>%
  na.omit()

#get the most recorded countries
popular5countryfind <- interestedvars %>% 
  group_by(country) %>% 
  summarise(n = n()) %>% 
  as.data.frame() %>% 
  arrange(., desc(n)) %>% 
  head(5)

wine_selectcountry <- interestedvars %>% 
  mutate(year = as.numeric(year), 
         price = as.numeric(price),
         variety = as.factor(variety),
         country = as.factor(country)) %>%
  filter(country %in% popular5countryfind$country) %>%
  mutate(country = factor(country),
         variety = factor(variety)) %>% #when subsetting, factor levels remain  
  distinct() %>% 
  sample_n(1500) #too large data structure otherwise 


#make plots for EDA (presentation)
sm.density.compare(wine_selectcountry$points, wine_selectcountry$country, xlab = "Points Received")
legend("right", levels(wine_selectcountry$country), fill=2+(0:nlevels(wine_selectcountry$country)))

ggplot(wine_selectcountry, aes(y=wine_selectcountry$price)) + 
  geom_boxplot(aes(fill=wine_selectcountry$country)) + labs(fill='Country', y = "Price")

ggplot(wine_selectcountry, aes(y=wine_selectcountry$year)) + 
  geom_boxplot(aes(fill=wine_selectcountry$country)) + labs(fill='Country', y = "Year")

## Create dissimilarity matrix
d.wine <- daisy(wine_selectcountry, metric = "gower", stand = FALSE)
d.winemat <- as.matrix(d.wine)

## stat of matrix 
mean(d.winemat)
median(d.winemat)

## create edge matrix 

#initialize edge matrix with placeholders
d.winemat.edge <- matrix(rep(0, 1500^2), nrow = 1500, ncol = 1500)
  
for(i in 1:1500){
  for(j in 1:1500){
    d.winemat.edge[i,j] = ifelse(d.winemat[i,j] < 0.60, 0, 1)
  }
}
# tried parameters 0.3*, 0.35*, 0.59 (2 clusters), 0.61*, 0.65* (* = each observation own cluster)
mean(d.winemat.edge)

## uncomment if you want countries in plot
## but I have commmented it here bc I cannot plot 
## the exceedingly large file

# colnames(d.winemat.edge) = wine$country
# rownames(d.winemat.edge) = wine$country


# make into adjacency list for by-cluster summary stats
# wine.diss <- data.frame(wine1=rownames(d.winemat.edge)[row(d.winemat.edge)], wine2=colnames(d.winemat.edge)[col(d.winemat.edge)], dist=c(d.winemat.edge)) 
# 
# wine.diss <- wine.diss %>%
#  mutate(edge = ifelse(wine.diss$dist < firstq, 0, 1))

# make graph object of country data
g_country <- graph_from_adjacency_matrix(d.winemat.edge, mode="upper")
# don't run this... too big, will crash R: plot(g_country)

# run thru alg 1 walktrap
wt <- walktrap.community(g_country)
sizes(wt)
modularity(wt)

# Summary stats by Cluster

# wine$cluster <- as.factor(fc$membership)
#  wine %>% 
#   group_by(cluster) %>% 
#   summarise(mean_price = mean(price),
#             mean_year = mean(year),
#             mean_points = mean(points))
# 
# #population means 
# mean(wine$price)
# mean(wine$year)
# mean(wine$points)


# alg 2 
# see below section 
# ebc <- edge.betweenness.community(g_country)
# sizes(ebc)
# not working because beyond the upper limit bound

# alg 3
fc <- cluster_fast_greedy(g_country)
sizes(fc)
modularity(fc)

# alg 4 
spin <- spinglass.community(g_country)
sizes(spin)

# alg 5
ec <- leading.eigenvector.community(g_country)
sizes(ec)
modularity(ec)

# alg 6
lp <- label.propagation.community(g_country)
sizes(lp)

# Comparing the groups

# Kelly will insert the tables of the sizes here
WT <- as.vector(membership(wt))
EBC <- as.vector(membership(ebc))
FC <- as.vector(membership(fc))
SPIN <- as.vector(membership(spin))
EC <- as.vector(membership(ec))
LP <- as.vector(membership(lp))


ec_wt <- tally(~EC + WT); ec_wt
ec_ebc <- tally(~EC + EBC); ec_ebc
ec_fc <- tally(~EC + FC); ec_fc
ec_spin <- tally(~EC + SPIN); ec_spin
ec_lp <- tally(~EC + LP); ec_lp
```


### All for EBC
```{r}
wine_orig <- read_csv("winemag-data-130k-v2.csv")
#complete_cases_wine <- na.omit(wine)
#complete_case_wine_count <- nrow(complete_cases_wine)

interestedvars <- wine_orig %>%
    mutate(year = str_extract(wine_orig$title, "[1|2][0|1|9][0-9][0-9]")) %>%
  select(price, year, variety, country, points) %>%
  na.omit()

#get the most recorded countries
popular5countryfind <- interestedvars %>% 
  group_by(country) %>% 
  summarise(n = n()) %>% 
  as.data.frame() %>% 
  arrange(., desc(n)) %>% 
  head(5)

wine_selectcountry_small <- interestedvars %>% 
  mutate(year = as.numeric(year), 
         price = as.numeric(price),
         variety = as.factor(variety),
         country = as.factor(country)) %>%
  filter(country %in% popular5countryfind$country) %>%
  mutate(country = factor(country),
         variety = factor(variety)) %>% #when subsetting, factor levels remain  
  distinct() %>% 
  sample_n(700) #too large data structure otherwise 


#make plots for EDA (presentation)
# sm.density.compare(wine_selectcountry$points, wine_selectcountry$country, xlab = "Points Received")
# legend("right", levels(wine_selectcountry$country), fill=2+(0:nlevels(wine_selectcountry$country)))
# 
# ggplot(wine_selectcountry, aes(y=wine_selectcountry$price)) + 
#   geom_boxplot(aes(fill=wine_selectcountry$country)) + labs(fill='Country', y = "Price")
# 
# ggplot(wine_selectcountry, aes(y=wine_selectcountry$year)) + 
#   geom_boxplot(aes(fill=wine_selectcountry$country)) + labs(fill='Country', y = "Year")
# 
## Create dissimilarity matrix
d.wine.small <- daisy(wine_selectcountry_small, metric = "gower", stand = FALSE)
d.winemat.small <- as.matrix(d.wine.small)

## stat of matrix 
mean(d.winemat.small)
median(d.winemat.small)

## create edge matrix 

#initialize edge matrix with placeholders
d.winemat.small.edge <- matrix(rep(0, 700^2), nrow = 700, ncol = 700)
  
for(i in 1:700){
  for(j in 1:700){
    d.winemat.small.edge[i,j] = ifelse(d.winemat.small[i,j] < 0.70, 0, 1)
  }
}
# tried parameters 0.3*, 0.35*, 0.59 (2 clusters), 0.61*, 0.65* (* = each observation own cluster)
mean(d.winemat.small.edge)

## uncomment if you want countries in plot
## but I have commmented it here bc I cannot plot 
## the exceedingly large file

# colnames(d.winemat.edge) = wine$country
# rownames(d.winemat.edge) = wine$country


# make into adjacency list for by-cluster summary stats
# wine.diss <- data.frame(wine1=rownames(d.winemat.edge)[row(d.winemat.edge)], wine2=colnames(d.winemat.edge)[col(d.winemat.edge)], dist=c(d.winemat.edge)) 
# 
# wine.diss <- wine.diss %>%
#  mutate(edge = ifelse(wine.diss$dist < firstq, 0, 1))

# make graph object of country data
g_country.small <- graph_from_adjacency_matrix(d.winemat.small.edge, mode="upper")
ebc <- edge.betweenness.community(g_country.small)
sizes(ebc)


ec.small <- leading.eigenvector.community(g_country.small)
sizes(ec.small)
modularity(ec)

EBC <- as.vector(membership(ebc))
EC.small <- as.vector(membership(ec.small))

ec_ebc <- tally(~EC.small + EBC); ec_ebc
```
